### 2023-07-12 intro.tex

The developments in Section~\ref{sec:calculus} support the intuition (remarked upon by \citet{Localinf} and \citet{BidirTyping}) that local type inference pairs well with type error localization and recovery because information flows systematically and locally through the tree. However, many functional languages including Elm, OCaml and Haskell feature constraint-based type inference, with constraints gathered globally. For type systems where inference is decidable, this is powerful, but it is also notorious for complicating error localization, because inconsistencies can arise through a confluence of constraints originating from any number of locations.

>>>>

The developments in Section~\ref{sec:calculus} support the intuition (remarked upon by \citet{Localinf} and \citet{BidirTyping}) that local type inference pairs well with type error localization and recovery because information flows systematically and locally through the tree. However, many functional languages including Elm, OCaml and Haskell feature constraint-based type inference, with constraints gathered globally. For type systems where inference is decidable, this is powerful, but it is also notorious for complicating error localization, because inconsistencies can arise through a confluence of constraints originating from any number of locations \cite{DBLP:conf/popl/Wand86}.
